
\documentclass[11pt, oneside]{article}
\usepackage[margin=0.5in]{geometry}
\geometry{letterpaper}           
\usepackage[parfill]{parskip}    
\usepackage{graphicx}				
\usepackage{amssymb}
\usepackage{xcolor}
\pagecolor{white}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue]{hyperref}
\pagestyle{empty}

\title{Jacob Bartlett}
\author{Jacob Bartlett}

\begin{document}

\begin{center}
\section*{Jacob Bartlett}
Mobile Engineering Lead

\href{jacobmartinbartlett@gmail.com}{jacobmartinbartlett@gmail.com}
\end{center}

\subsection*{Profile}

Award-winning full-stack mobile engineering leader with a strong product focus. Co-founder of Carbn, the world's top-rated climate action app. Currently Mobile Engineering Lead at a rapidly-growing scale-up, Gener8. Over 9 years of experience building production systems across the tech stack – from iOS and Android apps to infra, APIs, and databases. Active \href{https://nslondon.com/#jacob-bartlett-clean-networking-with-combine}{conference speaker} and \href{https://jacobbartlett.substack.com}{technical blogger}.

\medskip
\subsection*{Experience}

\textbf{Gener8}
\hfill
\textit{July 2022 – Present}

\textbf{Mobile Engineering Lead}

\begin{itemize}
  \item Spearheaded the mobile engineering team at Gener8, where our \href{https://apps.apple.com/app/gener8-earn-from-your-data/id1586631181}{iOS} and \href{https://play.google.com/store/apps/details?id=com.gener8ads.wallet}{Android} apps were rated over 4.7* with over 100,000 downloads.
  \item Managed a talented and lean engineering team distributed across several countries.
  \item Took ownership over delivery of our behind-schedule MVPs. Outlined a delivery plan with the CEO, and executed on it to get both apps released within my first 3 months.
  \item Established consensus within the engineering organisation on high-level technical system designs.
  \item Developed a highly complex, performant SwiftUI app with 16 modules and over 85\% unit test coverage.
  \item Implemented cross-platform, offline-first end-to-end testing across iOS and Android using Maestro and an NodeJS mock server.
  \item Built an iOS Safari Extension which had a 1-month retention rate of 75\%.
  \item Created a release health dashboard, which automatically ran SQL queries for various key metrics, by app version, to rapidly alert us to issues and catching production incidents. 
  \item Acted as hiring manager to bring top-tier mobile engineering talent into the business.
  \item Reported directly to the CTO while actively contributing to iOS and Android app development.
\end{itemize}

\medskip

\textbf{Carbn}
\hfill
\textit{August 2020 – July 2022}

\textbf{Co-Founder}

\begin{itemize} 
  \item Test
\end{itemize}

\medskip

\textbf{Deloitte Digital}
\hfill
\textit{June 2016 – August 2020}
								 
\textbf{iOS Software Engineer}

\begin{itemize}
  \item Built 20+ apps across various industries, specialising in Swift and ensuring knowledge sharing across my organisation.
  \item Raised the UK's COVID-19 testing throughput to 500k per day by developing the networking and architecture for the NHS COVID-19 testing program apps. Won the \href{https://apps.apple.com/app/carbn/id1533681322}{BIMA10 mobile app award} for these efforts.
  \item Collaborated with AWS as an iOS specialist to creating a seamless networking layer (merging BLE and cellular) for a UK electric car venture.
  \item Developed an complex CI/CD pipeline on Fastlane to improve code quality, reduce rework, and save 10-20 cumulative hours of developer time per sprint for an AI-based banking project.
  
\end{itemize}

\medskip

\subsection*{Education}
\textbf{Quantic School of Business and Technology}
\hfill
\textit{MBA – Honors (Top 10\%) – 2021}

Gained expertise in Accounting, Finance, Marketing, Operations, and Entrepreneurship, and built a robust professional network to secure Angel investors for Carbn.

\medskip

\textbf{Imperial College London}
\hfill
\textit{BSc Physics – 1st Class – 2016}

Concentrated on computing, astrophysics, quantum mechanics, and theoretical particle physics, culminating in a dissertation on "Computational Evolution" that leveraged unsupervised machine learning algorithms to analyze life evolving across 1 million generations.

\end{document}  
